\documentclass[classic]{moderncv}

% moderncv styles
\moderncvstyle{casual}

% character encoding
\usepackage[utf8]{inputenc}

% personal data
\firstname{Xavier}
\familyname{Danaux}
\title{Dynamic and innovative engineer/jurist}
\address{234 rue de l'infante, B-1410 Waterloo}
\phone{+12 (3)456 78 90 12}
\email{xdanaux@gmail.com}
\extrainfo{{\small single with driver licence}}
\quote{Am willing to tear down walls, build bridges, and light fires.\\I have no real experience, but lots of energy, a bit of that ``vision thing'',\\and I'm not afraid to start from the beginning.}

%\renewcommand{\listsymbol}{{\fontencoding{U}\fontfamily{ding}\selectfont\tiny\symbol{'102}}}
\definecolor{see}{rgb}{0.5,0.5,0.5}

% command for text subscripts
\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}

% the ConTeXt symbol
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}

% slanted small caps (only with roman family; the sans serif font doesn't exists :-()
%\usepackage{slantsc}
%\DeclareFontFamily{T1}{myfont}{}
%\DeclareFontShape{T1}{myfont}{m}{scsl}{ <-> cork-lmssqbo8}{}
%\usefont{T1}{myfont}{m}{scsl}Testing the font


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle%
\makequote%
%
\section{Strengths}
\cvresume{Soon-to-be mechanical engineer specialized in computational fluid dy\-na\-mics, with a good legal education.}{Likes practicing adventure sports like skying, rock climbing and scuba diving, and has been a boy scout for five years.}
\cvresume{Leadership skills.}{Open minded and eager to learn.}
\cvresume{Photography and design enthusiast.}{Creative with a strong analytical mind.}
\cvresume{Loves to tackle complex problems.}{World citizen.}
%
\section{Education}
\cventry{2003--current}{Master of Science in Mechanical Engineering}{Université catholique de Louvain}{}{}{1\up{st} year: 82\%\hspace{2em}2\up{nd} year: 74\%\hspace{2em}3\up{rd} year: --- (currently being assessed)}
\cventry{2005--current}{Master of Laws}{Université catholique de Louvain}{}{}{1\up{st} year: --- (currently being assessed)}
\cventry{2003--2005}{Bachelor of Laws}{Université catholique de Louvain}{}{}{1\up{st} year: 70\%\hspace{2em}2\up{nd} year: 67\%}
\cventry{2001--2003}{Bachelor of Science}{Université catholique de Louvain}{}{}{1\up{st} year: 74\%\hspace{2em}2\up{nd} year: 76\%}
%\cventry{1995--2001}{High School Degree, Latin--Math orientation}{Collège Saint-Michel d'Etterbeek}{}{}{}
%\cventry{1989--1995}{Primary School Degree}{Sint-Jozefscollege te Sint-Pieters-Woluwe}{}{}{}
%
\section{Master thesis}
\cvitem{title}{\emph{On the rheology of entangled polymers}}
\cvitem{supervisors}{Pr Christian Bailly and Pr Roland Keunings}
\cvitem{description}{\small Study of the complex behaviour of viscoelastic fluids, and in particular of entangled polymers.\\The study is focused on double-step strain and recoil deformations, comparing experimental data to simulations based on recent microstructural models.
Depending on the model used, numerous mathematical tools are used: numerical solving of nonlinear PDEs, stochastic equations, Monte-Carlo simulations, Fourier transforms, \dots{}}
%
\section{Experience}
\cventry{april 2004--\\current}{Administrator}{Alterezo ASBL}{Liège}{}{Nonprofit association aimed at helping small organizations access mo\-dern com\-mu\-ni\-ca\-tion tools via the internet, and promoting the use of open sour\-ce so\-lu\-tions and open standards.\newline{\itshape\color{see}\footnotesize{}See \httplink{www.alterezo.be}.}}
\cventry{2005--2006}{Mathematics tutor}{UCL}{Louvain-la-Neuve}{}{Supervision of practical sessions for a mathematical course given to second year engineering students (course \emph{FSAB1104: Numerical Methods}).\newline{\itshape\color{see}\footnotesize{}See \httplink{www.legat-online.be/b2q1/num}.}}
\cventry{2004--2006}{Cultural project leader}{Tchouque-Tschouk Kot}{Louvain-la-Neuve}{}{Leader of a student home with a cultural project, requiring day to day management as well as the organization of public events.\newline{\itshape\color{see}\footnotesize{}See \httplink{www.organe.be}.}}
%\cventry{1999--2003}{Student jobs}{}{}{}{Various student jobs, ranging from sport monitor and birthday animator for kids (Action Sport ASBL, 1999--2001) to tank station employee (Shell-Gecafin, august 2002 and september 2003) or receptionist (Randstad S.A., august 2001).}
\cventry{1999--2001}{IMO preselected}{SBPMef}{Wépion}{}{Advanced mathematical training, as Belgian preselected candidate for the International Mathematical Olympiads, selected by the Belgian mathematical society.\newline{\itshape\color{see}\footnotesize{}See \weblink{imo.math.ca/belgium.html}.}}
%
\section{Languages}
\cvlanguage{French}{Native}{}
\cvlanguage{Dutch}{Near-native}{Primary education degree obtained in a Dutch college\\(Sint-Jozefscollege te Sint-Pieters-Woluwe).}
\cvlanguage{English}{Very good}{Many journeys in English speaking countries, including the United States, the United Kingdom and Kenya.}
\cvlanguage{Chinese}{Elementary}{Following official courses at the ``Institut des Langues Vivantes'' (UCL), for the second year now.}
%
\section{Computer skills}
\cvcomputer{OS}{Linux, Unix, MacOS, Windows}{desktop}{OpenOffice, StarOffice, MS Office}
\cvcomputer{programming}{\textsc{Java}, C/C++}{scripting}{PHP, Shell, Ruby}
\cvcomputer{scientific}{Matlab, Autocad, Abaqus}{typography}{\LaTeX, \ConTeXt, Scribus, QuarkXPress}
\cvcomputer{web design}{XHTML, CSS, AJAX}{database}{MySQL, PostgreSQL}
\cvcomputer{administration}{Apache, Mailman}{}{}
%
\end{document}
